Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
quick pass up to (excluding) 5.2

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the key issues of prior work. We conducted a comprehensive
study involving \numFaults{} faults from \numPrograms{} different
programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. Results show that \ds{} misses
faulty statements in $9\%$\comments{(23 misses)} of the \numFaults{}
faults analyzed. Furthermore, we found that the combination of the two
approaches may improve fault localization up to $73.7\%$ (\avgImprov\ on average).
 To sum, results indicate that the
risk of applying the technique is relatively low for the positive
impact it may bring; and, the tool implementing the technique works
out-of-the-box, \ie{}, it puts no requirements on the running
environment, subject programs it can be used, and requires no special
setup.

@@

Model-based diagnosis is a well-known approach that has been proposed by the
DX community, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.

@@

We used subject programs from the \dfj{}
benchmark~\cite{just-defects4j-issta2014} in our evaluation.
Table~\ref{tab:df4j} shows size, number of tests, and number of
faults, for each considered program. $2$ subjects from Math
were not considered because we were not able to reproduce them
in the machine used for the experiments.

@@

\lang{} is a
library that provides a set of helper utilities for the
{\small\texttt{java.lang}} API. \cmath{} is a lightweight library of
self-contained mathematics and statistics components.\comments{ The
  \closure{} is a toolset for turning JavaScript files into smaller
  scripts for faster download and execution in the browser.} \chart{}
is a Java library for creating charts.  \jtime{} is a lightweight
library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler
APIs. \mockito{} is a mocking testing framework.

@@

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\cite{Pearson:2017:EIF:3097368.3097441}.
A fault of omission (\foo) occurs when
the program is buggy because some code is missing, i.e., a bug that is
corrected by adding code. Intuitively, the ability of techniques to
produce accurate diagnostic reports in those cases might be poor since
fault of omission bugs are very difficult to locate. This dataset has a
total of $59.7\%$ of \foo s which may contribute negatively to our
results since \sfl{} strives to rank these cases.
%in producing
%high-qualitiy diagnosis.

%\subsection{Experimental Methodology}
%\label{sec:methodology}

\subsection{Techniques}
One important independent variable for this study is the scope of
dynamic slicing. Slicing the entire code would be unacceptably
expensive as Critical Slicing needs to re-compile the affected file at
every iteration, \ie{}, after deleting statements and before checking
the oracle (see Section~\ref{sec:slicing}). We control the scope of
slicing through the variable $k$, which denotes the number of distinct
files that dynamic slicing will minimize. In this study, we used $5$ and
$10$ as the values of $k$, following the same values as in previous fault
localization studies~\cite{ang-perez-van-deursen-rui-2017}.
The $k$ files for minimization are selected
from the \sfl{} ranking as follows. First, we build a rank of files by
determining, for each ranked statement, the file that declares
it. Then, we select the top $k$ distinct files from such file ranking.

>>>>

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the key issues of prior work. We conducted a comprehensive
study involving \numFaults{} faults from \numPrograms{} different
programs from the Defects4J (D4J)
benchmark~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. Results show that \ds{} misses
faulty statements in $9\%$\comments{(23 misses)} of the \numFaults{}
faults analyzed. Furthermore, we found that the combination of the two
approaches may improve fault localization up to $73.7\%$
(\avgImprov\ on average).\Mar{do we have supporting data to say that
  the improvement is bigger when we care the most? for the cases SFL
  performs worse? if yes, can we show average for that?} To sum, results indicate that the
risk of applying the technique is relatively low for the positive
impact it may bring; and, the tool implementing the technique works
out-of-the-box, \ie{}, it puts no requirements on the running
environment, subject programs it can be used, and requires no special
setup.

@@

Model-based diagnosis is a well-known approach that has been proposed by the
DX community\Mar{I don't know what is DX. suggest to expand the
  acronym and/or cite.}\Mar{say shortly (in general terms) what is the
  goal. what is that good for.}, a sub-field of AI~\cite{REITER198757,DEKLEER200325}. Applications
of model-based diagnosis to localize software faults have demonstrated that it
can be framed as dynamic slicing~\cite{Mayer:2008:EMM:1642931.1642950,mayer2008prioritising}.

@@

We used subject programs from the \dfj{}
benchmark~\cite{just-defects4j-issta2014} in our evaluation.
Table~\ref{tab:df4j} shows size, number of tests, and number of
faults, for each considered program. Two faults from \cmath{} were not
considered because we were unable to reproduce them in our
environment.

\lang{} is a library providing utility functions for the
     {\small\texttt{java.lang}} API. \cmath{} is a library of
     self-contained mathematics and statistics components.\comments{
       The \closure{} is a toolset for turning JavaScript files into
       smaller scripts for faster download and execution in the
       browser.} \chart{} is a Java library for creating charts.
     \jtime{} is a library for manipulating date and time\comments{,
       providing a simpler API compared to
       {\small\texttt{java.util.Date}}}. \mockito{} is a mocking
     testing framework.

@@

@@

As to quantify complexity of fault localization on this benchmark, we
counted the number of cases of ``fault of omission'', a popular metric
in fault localization research for that
purpose~\cite{Pearson:2017:EIF:3097368.3097441}.  A fault of omission
(\foo) occurs when the program is buggy because some code is missing,
i.e., a fix to the bug iss created by adding code as opposed to
modifying or changing code. Intuitively, the ability of techniques to
produce accurate diagnostic reports in those cases might be poor as
techniques can only extract information about existing statements,
which are not problematic. This dataset has a total of $59.7\%$ of
\foo s, making it challenging for techniques to perform
well. \Mar{Sofia, does it make sense to show a histogram of (initial)
  rankings of pure SFL to complement this argument? Say, frequency of
  cases SFL reports on <top-10 statements in the ranking, then
  frequency within top-10> and <top-20, etc.}

\subsection{Techniques}
\Mar{---------------------- estou aqui}

One important independent variable for this study is the scope of
dynamic slicing. Slicing the entire code would be unacceptably
expensive as Critical Slicing needs to re-compile the affected file at
every iteration, \ie{}, after deleting statements and before checking
the oracle (see Section~\ref{sec:slicing}). We control the scope of
slicing through the variable $k$, which denotes the number of distinct
files that dynamic slicing will minimize. In this study, we used $5$ and
$10$ as the values of $k$, following the same values as in previous fault
localization studies~\cite{ang-perez-van-deursen-rui-2017}.
The $k$ files for minimization are selected
from the \sfl{} ranking as follows. First, we build a rank of files by
determining, for each ranked statement, the file that declares
it. Then, we select the top $k$ distinct files from such file ranking.
